---
title: "Paper"
author: "Ben Czekanski"
date: "April 24, 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(knitr)
library(ws.data)
library(dplyr)
library(lubridate)
library(zoo)
library(RcppRoll)
library(ggplot2)
library(reshape)
#Dont want to use reshape long term
library(tidyr)
library(project7)
library(htmlTable)
```

```{r}
x <- get_data()

y <- x %>%
  filter(symbol == "AAPL"| symbol =="MSFT"| symbol =="GOOG" | symbol == "FSLR" | symbol == "AMZN" | symbol == "GAP" | symbol == "G.1" | symbol == "NSCN" | symbol == "NKE" | symbol == "NDAQ" | symbol == "PMI"| symbol == "ACS" | symbol == "ACV")
### UNdo this

z <- compute_ret(y)



w <- do_rank(z)

v <- tbl_one(w)
htmlTable(txtRound(v, 2))
```


    htmlTable(t,
              rgroup = c(3, 6, 9, 12),
              n.rgroup = c(4, 4, 4, 4)
              
              )

```


tbl_1_data <- select_data(v, c(3, 6, 9, 12), c(3, 6, 9, 12))
tbl_1 <- make_table1(tbl_1_data)
kable(tbl_1)
# Table 2
tbl_2_data <- select_data(z, c(3, 6, 9, 12), c(12, 24, 36))
tbl_2 <- make_table1(tbl_2_data)
# needs size
kable(tbl_2)
# Table 3
tbl_3_data <- select_data(z, c(3, 6, 9, 12), c(3, 6, 9, 12))
tbl_3 <- make_table2(tbl_3_data)
kable(tbl_3)
# Table 4



# Table 5
tbl_5_data <- select_data(z, c(3, 6, 9, 12), c(12, 24, 36))
tbl_5 <- make_table2(tbl_5_data)
kable(tbl_5)
# Table 6
tbl_6_data <- select_data(z, c(3, 6, 9, 12), c(1:48))
tbl_6 <- make_table6(tbl_6_data)
kable(tbl_6)
# Needs Price and N

# Table 7




